Binary companions of red giant stars in \apogee\ \DR

### 2018-02-28 paper/1-catalog/twoface-catalog.tex
Err small edits

We don't expect there to be a sharp transition in orbital parameters between
stars with companions and stars without companions: There is a continuum of
companion properties.
For example, the companion masses can be low mass, or at long periods, or at
high inclination, all of which will make the velocity semi-amplitude, $K$, small
for a given system.
From the radial velocity data alone, there is therefore no way to define a
simple cut to select a complete sample of stars with companions.
Nevertheless, it is possible to define a cut that selects stars with
high-confidence companions.

>>>>

We don't expect there to be a sharp transition in orbital parameters between
stars with companions and stars without companions: There is a continuum of
companion properties.
For example, the companion masses can be low mass, or at long periods, or at
high inclination, all of which will make the velocity semi-amplitude, $K$, small
for a given system.
Therefore, from the radial velocity data alone, there is no way to define a
simple cut to select a complete sample of stars with companions.
It is nevertheless possible to define a cut that selects stars with
high-confidence companions.
